Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-06 analysis/paper/paper.Rmd
add an equivalence test figure, not complete

>>>>

```{r equivalence-tests, echo=FALSE, warning=FALSE, message=FALSE}
a <- plot(equivalence_test(m_f1), rope_color = "grey70") +
  scale_y_discrete(
    label = function(x) {
      x %>% gsub("b_abbreviation", "", .)
    }
  ) +
  scale_fill_grey()
b <-
  plot(equivalence_test(m_f2), rope_color = "grey70") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  scale_fill_grey()
c <-
  plot(equivalence_test(m_f3), rope_color = "grey70") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  scale_fill_grey()

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))

```
